Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
small changes to some code

<!-- Practice Code -->

```{r practice code}

@@

<!-- Main page Chart with All Personas -->

Market Share
--------------------------------------

```{r plot all personas}

@@

<!-- Persona and Organizational Tabs -->

Personas And Organizations {.tabset .tabset-fade}
--------------------------------------------------

>>>>

<!-- Practice Code -->
```{r practice code}

@@

<!-- Main page Chart with All Personas -->
Market Share
--------------------------------------

```{r global plot}

@@

<!-- Persona and Organizational Tabs -->
Personas And Organizations {.tabset .tabset-fade}
--------------------------------------------------
